### 2020-08-21 Analysis/Code/Paper.Rmd
sample

 author: "Dmitry Sorokin"
 date: "`r format(Sys.time(), '%B %d, %Y')`"
 classoption: pagebackref # passes pagebackref=true to hyperref before it is loaded, allowing backreferencing
 output:
  pdf_document:
    keep_tex: true
    fig_height: 2.5
    fig_width: 6
    number_sections: true
    citation_package: natbib
    extra_dependencies:
       footmisc: ["bottom"] # footnote management
       setspace: ["doublespacing"] # spacing of the paper
       caption:
       dsfont: null # indicator function 1
       booktabs: null
       makecell: null
    includes:
       in_header: extra_header.tex
  html_document:
    fig_height: 2.5
    fig_width: 6
    number_sections: true

@@

# Score and reviews variables are now 1{score is defined} x Var. This allows to 
# run regressions without excluding observations with < 10 reviews, for which the 
# score variable is, technically, undefined.
panel[noScore==T, score := 0]
# panel[noScore==T, reviews := 0]

@@

panel[, pRevRate := max(pReviews,na.rm = T)/max(age, na.rm = T), by = ID]
panel[, nRevRate := max(nReviews,na.rm = T)/max(age, na.rm = T), by = ID]

R.low <- 0.4
R.high <- 0.7
panel[score < R.high*100 & score >= R.low*100,
      needPos := ceiling((R.high*reviews-pReviews)/(1-R.high))]
panel[score < R.high*100 & score >= R.low*100,
      needNeg := floor(abs((R.low*reviews-pReviews)/(1-R.low)))+1]
# corrects for the rounding error caused by machine precision division of, say, 4/10 != 0.4. If you are supposed to be brought exactly to the cutoff, your needNeg is one review more than that
panel[(pReviews - needNeg)/(reviews-needNeg) == R.low & needNeg > 0,  needNeg := needNeg + 1]

@@

table <- texreg(res,
                stars = c(0.01, 0.05, 0.1),
                digits = 3,
                custom.model.names = c("NLLS", "Reg", "Ideal Reg"),
                reorder.coef = c(1, 2, 6, 7, 8, 9, 10, 11, 5, 12, 3, 4, 13, 14),
                caption = "Estimates of the Demand Parameters",
                caption.above = T,
                label = "demandEstimates")

@@

Column “NLLS” in Table \ref{demandEstimates} presents the estimates of the demand parameters in (\ref{arrivalReg}), and column “Reg” presents the results of estimating the log-regression (\ref{logReg}) with the same set of covariates; finally, column “Full Reg” reports the results of estimating the log-regression with the ideal set of covariates (using week effects instead of the Seasonal Sale dummy). It is readily checked that the difference between the preferred log-regression in column 3 and its restricted analog in column 2 is very small. The $R^2$ statistic confirms that week effects do not contribute much to explaining the data, and I conclude that the Seasonal Sale dummy captures the main time-specific shocks well. Thus, it is reasonable to say that the omission of the week effects from the nonlinear Model (\ref{arrivalReg}) comes at little cost.  Now we can concentrate on the estimates of the demand parameters in (\ref{arrivalReg}), presented in the first column, and compare them with the heuristic regression results in the second or third column.

@@

The second imprortant set of variables are the price variables.

@@

```{r}
# Notice that rhoPosD is the sum of the parameters I defined
# in the text, rho_0i^+ and rho_1i^+, but the variance matrix is
# calculated for the original parameters
panel[, disc:=c(shift((discount > 0))),
      by = ID][is.na(disc), disc := F]
revs <- panel[, .(t, disc, lambda, l = c(pReviews[1], diff(pReviews)), d = c(nReviews[1], diff(nReviews))), by=ID]
revs <- revs[, .(rhoPosD = sum(disc*l) / sum(disc*lambda),
                 rhoPosND = sum((1-disc)*l) / sum((1-disc)*lambda),
                 rhoNegD = sum(disc*d) / sum(disc*lambda),
                 rhoNegND = sum((1-disc)*d) / sum((1-disc)*lambda)),
              by = ID]
revs <- revs[!is.na(rhoPosD)]

id.matrix <- matrix(c(1,0,0,1), nrow=2)
for (id in revs[, ID]){
   sums <- panel[ID==id, .(disc, lambda)][, sum(lambda), by = disc]

@@

```{r like-rates, fig.width = 8, fig.height = 6, include = F}
p1 <- ggplot(data = revs[posSignif==T, .(x = rhoPosD-rhoPosND)][x>=-0.5& x<=2,]) +
  ggtitle("Discount Contribution to Likes") +
  geom_histogram(mapping = aes(x = x, y = ..density..),
                 color = "black",
                 position = "identity",
                 boundary = 0,
                 alpha = 0.9,
                 binwidth = 0.25,
                 fill = my.colors[1]) +
  geom_density(mapping = aes(x = x),
                 color = "black",
                 position = "identity",
                 alpha = 0.4,
                 fill = my.colors[1]) +
  scale_x_continuous(name = "Change in Like Rates",
                     minor_breaks = NULL) +
  scale_y_continuous(name = NULL,
                     breaks = c(0, 1, 2),
                     minor_breaks = NULL) +
  my.theme() +
  coord_cartesian(xlim = c(-0.5, 2))

p2 <- ggplot(data = revs[posSignif==T, .(x = rhoNegD-rhoNegND)][x>=-0.5& x<=2,]) +
  ggtitle("Discount Contribution to Dislikes") +
  geom_histogram(mapping = aes(x = x, y = ..density..),
                 color = "black",
                 position = "identity",
                 boundary = 0,
                 alpha = 0.9,
                 fill = my.colors[1]) +
  geom_density(mapping = aes(x = x),
                 color = "black",
                 position = "identity",
                 alpha = 0.4,
                 fill = my.colors[1]) +
  scale_x_continuous(name = "Change in Dislike Rates",
                     minor_breaks = NULL) +
  scale_y_continuous(name = NULL,
                     minor_breaks = NULL) +
  my.theme() +
  coord_cartesian(xlim = c(-0.5, 2))

@@

```{r fig.cap='\\label{likeRatesPlot} Distributions of $\\rho_{1i}^+$ and $\\rho_{1i}^-$', fig.width=9}
ggarrange(p1, p2, nrow=1, align = "h")
```

>>>>

 author: "Dmitry Sorokin"
 date: "`r format(Sys.time(), '%B %d, %Y')`"
 classoption: pagebackref # passes pagebackref=true to hyperref before it is loaded, allowing backreferencing
 output:
  pdf_document:
    keep_tex: true
    fig_height: 2.5
    fig_width: 6
    number_sections: true
    citation_package: natbib
    extra_dependencies:
       footmisc: ["bottom"] # footnote management
       setspace: ["doublespacing"] # spacing of the paper
       caption: ["normal"]
       dsfont: null # indicator function 1
       booktabs: null
       makecell: null
    includes:
       in_header: extra_header.tex
  html_document:
    fig_height: 2.5
    fig_width: 6
    number_sections: true

@@

# Score and reviews variables are now 1{score is defined} x Var. This allows to 
# run regressions without excluding observations with < 10 reviews, for which the 
# score variable is, technically, undefined.
panel[noScore==T, score := 0]

@@

# the rates of review arrivals
panel[, pRevRate := max(pReviews,na.rm = T)/max(age, na.rm = T), by = ID]
panel[, nRevRate := max(nReviews,na.rm = T)/max(age, na.rm = T), by = ID]

# define how many positive and negative reviews are needed to transition, manualy
# for every threshold
R.low <- 0.4
R.high <- 0.7
panel[score < R.high*100 & score >= R.low*100,
      needPos := ceiling((R.high*reviews-pReviews)/(1-R.high))]
panel[score < R.high*100 & score >= R.low*100,
      needNeg := floor(abs((R.low*reviews-pReviews)/(1-R.low)))+1]
# corrects for the rounding error caused by machine precision division of, say, 4/10 != 0.4. If you are supposed to be brought exactly to the cutoff, your needNeg is one review more than that
panel[(pReviews - needNeg)/(reviews-needNeg) == R.low & needNeg > 0,  needNeg := needNeg + 1]

@@

table <- texreg(res,
                stars = c(0.01, 0.05, 0.1),
                digits = 3,
                custom.model.names = c("(1)", "(2)", "(3"),
                reorder.coef = c(1, 2, 6, 7, 8, 9, 10, 11, 5, 12, 3, 4, 13, 14),
                caption = "Estimates of the Demand Parameters",
                caption.above = T,
                label = "demandEstimates")

@@

Column (1) in Table \ref{demandEstimates} presents the estimates of the demand parameters in (\ref{arrivalReg}), and column (2) presents the results of estimating the log-regression (\ref{logReg}) with the same set of covariates; finally, column (3) reports the results of estimating the log-regression with the ideal set of covariates (using week effects instead of the Seasonal Sale dummy). It is readily checked that the difference between the preferred log-regression in column 3 and its restricted analog in column 2 is very small. The $R^2$ statistic confirms that week effects do not contribute much to explaining the data, and I conclude that the Seasonal Sale dummy captures the main time-specific shocks well. Thus, it is reasonable to say that the omission of the week effects from the nonlinear Model (\ref{arrivalReg}) comes at little cost.  Now we can concentrate on the estimates of the demand parameters in (\ref{arrivalReg}), presented in the first column, and compare them with the heuristic regression results in the second or third column.

@@

The second imprortant set of variables are the price variables. First row of Table \ref{demandEstimates} suggests that the price elasticity of demand of very low, between  `r round(-reg1$coefficients[2],2)` and `r round(-beta.hat[1],2)` in absolute value. This magnitude is very similar to the price elasticity that @ReimersWaldfogel20 finds studying reviews for books on Amazon.com. That paper argues that Amazon has been known to prioritize growth over profit, charging low prices and operating on the inelastic part of the demand curve. However, on Steam individual firms choose which prices to charge for their product, and they should have a stronger preference for profit than an entity that is a marketplace, rather than a seller. The situation becomes more clear after examining the coefficient on “New Discount”, an indicator variable for the first day after the discount\footnote{I found the effect to be stronger if a one day lag is allowed}. On average, a discount leads to a `r round(beta.hat[2]*100)`-`r round(reg2$coefficients[3]*100)`% spike in sales upon introduction. An average discount in the sample is `r round(panel[discount>0, mean(discount)]*100)`%, meaning that, based on the estimates in column 1, the effective change in quantity sold upon the introduction of the discount is `r round(beta.hat[2]*100)`%$+$`r round(-beta.hat[1]*round(panel[discount>0, mean(discount)]*100))`$%=$`r round(beta.hat[2]*100) + round(-beta.hat[1]*round(panel[discount>0, mean(discount)]*100))`%, with the effective elasticity of `r round((round(beta.hat[2]*100) + round(-beta.hat[1]*round(panel[discount>0, mean(discount)]*100)))/round(panel[discount>0, mean(discount)]*100),2)`. This number looks more reasonable, especially given that the products I study have a zero marginal cost of production, and in a static world firms would set prices at which the demand for their products would be unit-elastic. As I have mentioned in the Identification section, the the durable good nature of video games means that forward-looking behavior by the customers could lead to diff

@@

```{r}
# Notice that rhoPosD is the sum of the parameters I defined
# in the text, rho_0i^+ and rho_1i^+, but the variance matrix is
# calculated for the original parameters

# Shifting the variables because I am using lag k = 1
panel[, disc:=c(shift((discount > 0))), by = ID]
panel[, lam:=shift(lambda), by = ID]

revs <- panel[!(is.na(lam)), .(t, disc, lam, l = c(pReviews[1], diff(pReviews)), d = c(nReviews[1], diff(nReviews))), by=ID]
revs <- revs[, .(rhoPosD = sum(disc*l) / sum(disc*lam),
                 rhoPosND = sum((1-disc)*l) / sum((1-disc)*lam),
                 rhoNegD = sum(disc*d) / sum(disc*lam),
                 rhoNegND = sum((1-disc)*d) / sum((1-disc)*lam)),
              by = ID]
revs <- revs[!is.na(rhoPosD)]

id.matrix <- matrix(c(1,0,0,1), nrow=2)
for (id in revs[, ID]){
   sums <- panel[ID==id, .(disc, lam)][, sum(lam), by = disc]

@@

```{r like-rates, include = F}
p1 <- ggplot(data = revs[, .(x = rhoPosD-rhoPosND)][x>=-0.5& x<=2,]) +
  ggtitle("Discount Contribution to Likes") +
  geom_histogram(mapping = aes(x = x, y = ..density..),
                 color = "black",
                 position = "identity",
                 boundary = 0,
                 alpha = 0.9,
                 binwidth = 0.1,
                 fill = my.colors[1]) +
  geom_density(mapping = aes(x = x),
                 color = "black",
                 position = "identity",
                 alpha = 0.4,
                 fill = my.colors[1]) +
  scale_x_continuous(name = "Change in Like Rates",
                     minor_breaks = NULL) +
  scale_y_continuous(name = NULL,
                     breaks = c(0, 1, 2),
                     minor_breaks = NULL) +
  my.theme() +
  coord_cartesian(xlim = c(-0.5, 2))

p2 <- ggplot(data = revs[, .(x = rhoNegD-rhoNegND)][x>=-0.5& x<=2,]) +
  ggtitle("Discount Contribution to Dislikes") +
  geom_histogram(mapping = aes(x = x, y = ..density..),
                 color = "black",
                 position = "identity",
                 boundary = 0,
                 binwidth = 0.025,
                 alpha = 0.9,
                 fill = my.colors[1]) +
  geom_density(mapping = aes(x = x),
                 color = "black",
                 position = "identity",
                 alpha = 0.4,
                 fill = my.colors[1]) +
  scale_x_continuous(name = "Change in Dislike Rates",
                     minor_breaks = NULL) +
  scale_y_continuous(name = NULL,
                     minor_breaks = NULL) +
  my.theme() +
  coord_cartesian(xlim = c(-0.5, 2))

@@

```{r fig.cap='\\label{likeRatesPlot} Distributions of $\\rho_{1i}^+$ and $\\rho_{1i}^-$'}
ggarrange(p1, p2, nrow=1, align = "h")
```

```{r results = 'asis', warning = FALSE}
# remove 1% with the highest values of rho_1+ (<=2)
# and only keep significant coefficients
panel <- merge(panel, revs[, .(ID, rho1 = rhoPosD - rhoPosND, rhoPosD, rhoNegD)])

panel[, pos.treatment := (needPos <= 2*band)]
panel[, neg.treatment := (needNeg <= 2*band)]

reg1 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment +
               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
               mPositive + realPositive + vPositive + age + young + day + week,
           data = panel[rho1 <= 2 & rho1 >= -0.5 
                        # ID %in% revs[negSignif == T | posSignif == T, ID], 
                        ],
           model = "pooling")
cov<-vcovHC(reg1, method="white1")
se1 <- sqrt(diag(cov))

reg2 <- plm(I(discount>0) ~ rho1*pos.treatment + rho1*neg.treatment +
               log(needPosDays) + log(needNegDays) + poly(tWODisc, degree = 2) + log(reviews+1) + score +
               mPositive + realPositive + vPositive + age + young + day + week,
           data = panel[rho1 <= 2 & rho1 >= -0.5
                        # ID %in% revs[negSignif == T | posSignif == T, ID], 
                        ],
           model = "within")
cov<-vcovHC(reg2, method = "white1")
se2 <- sqrt(diag(cov))

star.out<-stargazer(reg1, reg2,
                    label = "rhoTransDiscReg",
                    header = FALSE,
                    title = "Discounts Before Potential Transitions And Firm Heterogeneity",
                    se=list(se1, se2),
                    dep.var.labels = c("$\\mathbb{P}(Discount)$"),
                    # column.labels=c("OLS", "Interaction", "FE", "FE: no $\\rho_{1i}^+$"),
                    model.numbers = F,
                    omit = c("tWODisc", "reviews", "noScore", "realPositive", 
                             "mPositive", "vPositive", "age", "young", "Constant",
                             "score", "day", "week", "needPosDays", "needNegDays"),
                    #covariate.labels = ,
                    order = c("rho1"),
                    omit.stat=c("f","adj.rsq","ser"),
                    no.space=T)
```
